s.function

### 2023-03-20 src/s_la_per_firm.Rmd
initial commit all outputs

@@

@@

```{r}
a.la <- as_tibble()
all.la <- df %>% filter(ladcd != "NA") %>% distinct(ladcd) %>% simplify2array()
simplify2array(all.la)

@@

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  dplyr::select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < 2003, "fast", "slow"))

@@

  xmid_la <- pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()
  lines <- data.frame(
    intercepts = c(2003, xmid_la[1]),
    Xmid = c("UK", i)
  )

@@

## Xmid frequency graph

**TO DELETE**, done it above.

```{r, eval=F}
# path.out <- paste0(path, "/outputs/xmid_f.png")
# 
# ggplot(a.la, aes(as.factor(round(estimate, 0)))) +
#   geom_bar(fill = "#0073C2FF") +
#   theme_minimal() +
#   ggtitle("Counts of Xmid per year") +
#   theme(plot.title = element_text(hjust = 0.5)) +
#   ylab("LAs") + xlab("year") 
# 
# ggsave(path.out)
```

@@

```{r eval=F}
path.out <- paste0(path, "/data/temp/s_la.csv")
write_csv(a.la, path.out)
```

>>>>

df <- df %>% filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

@@

xmid.uk <- tidy(fit) %>% filter(term=="xmid") %>% select(estimate) %>% as.numeric()

@@

```{r, eval=F}
a.la <- as_tibble()
all.la <- df %>% filter(ladcd != "NA") %>% distinct(ladcd) %>% simplify2array()
simplify2array(all.la)

@@

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  dplyr::select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < xmid.uk, "fast", "slow")) # it was 2003

@@

  xmid_la <- pred %>% left_join(a.la) %>% filter(ladcd == i) %>% dplyr::select(estimate) %>% first()
  lines <- data.frame(
    intercepts = c(xmid.uk, xmid_la[1]), # it was 2003
    Xmid = c("UK", i)
  )

@@

@@

```{r eval=F}
path.out <- paste0(path, "/data/temp/s_la_per_firm.csv")
write_csv(a.la, path.out)
```
